\documentclass[12pt]{article}

\usepackage{pdflscape}
\usepackage[margin=0.8in]{geometry}
\usepackage{graphicx} %Required for diagrams
\usepackage[hidelinks]{hyperref}
\usepackage{color}
\definecolor{myOrange}{RGB}{255, 165, 0}

\begin{document}

\input{./IEEE-SSCI_coverpage.tex}

\newpage


\pagebreak

\section{The Team}

% ================ BEGINING OF MY PART =========================

\subsection{Hlavutelo Maluleke}

\begin{description}
  \item[$\bullet$] A photo of yourself: From the group
  \subsubsection{Interests:}
  
   \item[$\bullet$] Coding (preferably in Java).
	 \item[$\bullet$] Developing random softwares (mostly in Windows).
	 \item[$\bullet$] I like Linux pretty much, it is the most beautiful platform for program design.
	 \item[$\bullet$] My other interest is to learn as many programming languages as possible.
	 \item[$\bullet$] Explore all different appraoches in software design.
	 \item[$\bullet$] Creating Android apps and iOS apps (very intruiging).
	 
	\subsubsection{Technical skills:}
	
	In COS 330, we studied about computer security, threats, vulnerabilities and counter-measures. These exposed us to various challenges in computer programming and how we can create a system with least vulnerabilities. We have used different programming languages to try accomplish systems with secure access. These skills enables me to solve major security issues.\\

	With regard to this project and in relation to my interests, I have quite good experience in Data structures (COS 212) which is basically Object oriented programming. From COS 121, design patterns have been covered very well and I have a clear understanding how they work. Moreover, I can use design patterns with data structures without any major problems. I am certain each of these will be required in the process of completing this project. For a more secure and efficient software data structures and design patterns must be implemented accordingly, so these skills will be required.
	
	\subsubsection{Any past experience which might be relevant for the project:}
	
	• Worked a bit with a friend who is currently working at The Innovation Hub, they mostly create Android apps. I have see seen mostly how they go about creating them. Though I have not yet implemented any working Android app before I believe with the minor experience I have I can explore many more other things. I believe this might be a bit of assistance to how we are supposed to code this app.
	
	\subsubsection{Non-technical strengths:}
	
	There are quite a couple of things that I am pretty good at, first is time management. I am able to manage my time under pressure or not. Secondly, working as a group is one of things I enjoy most, which I believe working as a collection can make our project more successful. I am very patient with one another, in this regard I am very open to other group members so as we can work consistently as a team.
	
	\subsubsection{What makes you want to do the project:}
	
	Security has been a major topic in almost all systems lately, weak systems are vulnerable to malware and other kinds of threats. As a result, most systems require a strong security that makes it hard for hackers to crack. Learning how to cease hackers is then an everyday job that every system developer/programmer should have massive experience in. This will expose me to some weak security measures and stronger security measures. Will this kind of knowledge, my services will be required in almost all various IT institutions.
	
	
	\end{description}
	
	% ======================= END OF MY PART =============================

\input{./TheTeam.tex}

\section{Project execution}


\end{document}