\documentclass[12pt]{article}

\usepackage{pdflscape}
\usepackage[margin=0.8in]{geometry}
\usepackage{graphicx} %Required for diagrams
\usepackage[hidelinks]{hyperref}
\usepackage{color}
\definecolor{myOrange}{RGB}{255, 165, 0}

\begin{document}

\input{./Mobile_Monitoring_Application_coverpage.tex}

\newpage


\pagebreak

\section{The Team}

% ================ BEGINING OF MY PART =========================

\subsection{Hlavutelo Maluleke}

\begin{description}
  \item[$\bullet$] A photo of yourself: From the group
  \subsubsection{Interests:}
  
  \item[$\bullet$] Coding (preferably in Java).
	 \item[$\bullet$] Developing random software (mostly in Windows).
	 \item[$\bullet$] I like Linux pretty much, it is the most beautiful platform for program design.
	 \item[$\bullet$] My other interest is to learn as many programming languages as possible.
	 \item[$\bullet$] Explore all different approaches in software design.
	 \item[$\bullet$] Creating Android apps and iOS apps (very intriguing).
	 
	 
	 \subsubsection{Technical skills:}
	 
	 With regard to this project and in relation to my interests, I have quite good experience in Data structures (COS 212) which is basically Object oriented programming. From COS 121, design patterns have been covered very well and I have a clear understanding how they work. Moreover, I can use design patterns with data structures without any major problems. I am certain each of these will be required in the process of completing this project. For a more secure and efficient software data structures and design patterns must be implemented accordingly, so these skills will be required.
	 
	 \subsubsection{Any past experience which might be relevant for the project:}
	 
	 • Worked a bit with a friend who is currently working at The Innovation Hub, they mostly create Android apps. I have see seen mostly how they go about creating them. Though I have not yet implemented any working Android app before I believe with the minor experience I have I can explore many more other things. I believe this might be a bit of assistance to how we are supposed to code this app.
	 
	 \subsubsection{Non-technical strengths:}
	 
	 There are quite a couple of things that I am pretty good at, first is time management. I am able to manage my time under pressure or not. Secondly, working as a group is one of things I enjoy most, which I believe working as a collection can make our project more successful. I am very patient with one another, in this regard I am very open to other group members so as we can work consistently as a team.
	 
	 \subsubsection{What makes you want to do the project:}
	
	Smartphones are arguably the most used devices in the entire world, communication is made easier with smartphones. As a software developer it is required to have knowledge in developing Android and iOS apps, a phone without any applications is only capable of making calls and text messages. To enhance your smartphone apps are a requirement. Hence, developers and programmers are at a demand and this project exposes us to be able to develop these apps. Learning experience gained from making these apps can be used in commercial companies that develop high rated applications. 
	
	
	\end{description}
	
	% ======================= END OF MY PART =============================

\input{./TheTeam.tex}

\section{Project execution}


\end{document}